---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rlsquiz: A flashcard and quiz app to learn Reef Life Survey habitat labels

<!-- badges: start -->
<!-- badges: end -->

The goal of rlsquiz is to facilitate learning local habitat labels based on a set of images. Habitat images and clickable label options are presented. Optionally, users can record quiz scores or add a folder of their own images and labels to learn.

This work is forked from: coralquiz by Matthew Doherty:  https://github.com/dohertyml/coralquiz. This version has been adapted to include RLS images, new folder structure, and renamed functions.

## Installation

You can install the development version of rlsquiz from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("njtierney/rlsquiz")
```

## Example


```{r example}
library(rlsquiz)
```

### Practice mode

Launch practice mode with `rls_practice`. The default folder for this is "rls_catalogue".  This launches the standard Reef Life Survey label scheme exemplar image set.

```r
rls_practice()
```

Launch the standard Reef Life Survey label scheme exemplar image set:

```r
rls_practice(source = "rls_catalogue")
```

Launch the Reef Repair Hub label scheme exemplar image set:

```r
rls_practice(source = "rls_RRH")
```

### Quiz mode 

This launches the standard Reef Life Survey label scheme exemplar image set with 20 questions

```r
rls_quiz()
```

Use the standard Reef Life Survey label scheme exemplar image set:

```r
rls_quiz("rls_catalogue", n = 20)   
```

Use the Reef Repair Hub label scheme exemplar image set:

```r
rls_quiz("rls_RRH", n = 20)   
```

##  Adding new image folders

Users can adapt this without code changes by referencing their own new top-level folder containing other labels and associated images. Requires ≥ 4 species per top-level folder, with sub-folders named as label names containing associated images. Supports jpg, jpeg, JPEG, png, webp. The folder will be automatically recognised when placed in the r package library under ...rlsquiz/app/www/photos. For example:

```r
rls_practice("*top-level folder*")
```

# Acknowledgements

Original coralquiz package by Matthew Doherty
Thanks for sharing the coralquiz framework that we adapted for Reef Life Survey habitats.
